---
title: "tppp"
author: "vg"
date: "26/09/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question 1 
```{r}
tab = read.table("immo.txt", header = TRUE,sep = ";")
tab
```



Price Value and Surface 
```{r}
plot(tab)
```
  Matrice de correlation
```{r}
cor(tab)
```
  

Les coeffecients de correlations sont proches de 1,lesdonnées sont très fortement corrélés

\mathbf{First model using OLS}

```{r}
Y = tab$prix
modreg = lm(prix~.,data = tab)
summary(modreg)
```

```{r}
betah = modreg$coefficients
betah
typeof(betah)
Bh = c(betah[1:3])
Bh = as.matrix(Bh)
dim(t(Bh))

```

```{r}
X = tab[c(1:2)]
X = cbind(rep(1,nrow(X)),X)
names(X)[1] = "cte"
X = as.matrix(X)
X
dim(X)
```

Calcul de Y hat
```{r}
Yhat = X%*%Bh
Yhat

{plot(Y,Yhat,panel.first = grid()) 
abline(0,1,col = 2,lty =2)}

```

difference predicted observation
```{r}
{plot(Y - Yhat)
abline(0,0,col = 2,lty = 2)}
```

Question d
```{r}
meany = mean(Y)
R2 = sum((Yhat-meany)**2)/sum((Y-meany)**2)

A = t(X)%*%X
B = t(X)%*%Y
beta2 = solve(A,B)
resb = cbind(beta2,Bh,beta2-Bh)
resb = as.table(resb)
colnames(resb)[1] = "Betah2"
colnames(resb)[2] = "Betah"
colnames(resb)[3] = "Betah2-betah"
resb
```


################################################################################################################################################################""
Exercice 2

a)

```{r}
tab = read.table("Icecreamdata.txt",header = T,sep = ";")
tab
```
```{r}
nobs = nrow(tab)
nobs
```

```{r}
plot(tab)
```
```{r}
cor(tab)
```
Regarding the previous and the correlation matrix we can say there aren't a linear relationship between them. However we can guess that the a correlation between the consumption and the temperature because $r = 0.775$  and the associated scatter plot follow a linear trend.

\mathbf{Formalization of the Problem}

We want to build a linear model between the ice consumption and the other co variables. Let's set:
$Y = (cons_i) $ avec $1 \leq i \leq 30$
$X = (income_i, price_i, temp_i)$ avec $1 \leq i \leq 30$
$\beta = (\beta_0 ,\beta_1,\beta_2,\beta_3) $ 

```{r}
Y = tab$cons
X = tab[2:4]
X = cbind(rep(1,nrow(X)),X)
names(X)[1] = "cte"
X
```

We are looking for $\beta$ so that $X\beta = Y$ 

b) \mathbf{Parameters estimation}
```{r}
modreg = lm(cons ~ ., data = tab)

summary(modreg)

```

```{r}
betah = modreg$coefficients
betah
```

The statistic test under $\mathbf{H}_0$ show that the variable "price" is less meaningful than "temp" and "income".


*** means we reject the test for error equal to 0.0001, ** for errors more or equal to 0.01 and * for errors more or equal to 0.05. 

Variable selection
```{r}
tab2 = tab
tab2 = tab2[-3]
tab2
modreg = lm(cons ~ ., data = tab2)
summary(modreg)
```
```{r}
betah2 = modreg$coefficients
Bh2 = c(betah2[1:3])
Bh2 = as.matrix(Bh2)
Bh2
```


```{r}
Y2 = tab2$cons
X2 = tab2[2:3]
X2 = cbind(rep(1,nrow(X2)),X2)
names(X2)[1] = "cte"


X2=as.matrix(X2)
X2
```



Calcul de $\^{Y}$
```{r}
Yhat = X2%*%Bh2
Yhat

{plot(Y,Yhat,panel.first = grid()) 
abline(0,1,col = 2,lty =2)}

```
Computation using matrix.
We assume that $X_2^TX_2$ is invertibe
```{r}
A = t(X2)%*%X2
B = t(X2)%*%Y2
beta2 = solve(A,B)
beta2
```
Computation of the $\^{Y}$
```{r}
Yhat = X2%*%beta2
{plot(Y,Yhat,panel.first = grid()) 
abline(0,1,col = 2,lty =2)}

```
Intervalle de confiance 

```{r}
confint(modreg,level = 1-2*0.05)
confint(modreg,level = 1-2*0.01)
confint(modreg,level = 1-2*0.001)

```

Predicted with $5%$
```{r}
newd =  data.frame(cbind((c(91,92,95,97)),(c(27,30,52,75))))
names(newd)[1:2] = c("income","temp")
yp = predict(modreg, newdata = newd, interval = "prediction",level = 0.05)
yp
library("plot3D")
plot(newd$income,yp[,1])
scatter3D(newd$income,newd$temp,yp[,1])
```









```{r}

#install.packages("leaps", dependencies = T)
#install.packages("matlib", dependencies = T)
library(leaps)
choix = regsubsets(cons ~ ., data = tab, nbest = 1, nvmax = 4)
summary(choix)
#plot(choix, scale = "bic")
#plot(choix, scale = "Cp")
choix
```





Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
